Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2022-05-13 reports/manuscript.Rmd
Fix link to table in text

```{r desctable, results="asis"}
reviews_tables$kable$table %>%
    kableExtra::row_spec(1:reviews_tables$kable$nrow, hline_after = TRUE) %>%
    kableExtra::row_spec(0, bold = TRUE) %>%
    kableExtra::column_spec(3:4, width = "2cm") %>%
    kableExtra::column_spec(5, width = "1.5cm") %>%
    kableExtra::column_spec(6:8, width = "3cm") %>%
    kableExtra::kable_styling(
        latex_options = c("repeat_header"),
        font_size = 5
    ) %>%
    kableExtra::landscape()
```

>>>>

```{r desctable}
reviews_tables$kable$data %>%
    knitr::kable("latex",
        caption = "Review characteristics for studies providing unique effects",
        col.names = c(
            "First Author", "Year", "Design Restrictions",
            "Regions Restrictions", "Study Range",
            "Sample Age Restrictions",
            "Outcomes Assessed", "Exposures Assessed"
        ),
        escape = FALSE,
        booktabs = TRUE,
        align = c("l", "c", "l", "l", "c", "l", "l", "l"),
        linesep = "",
        longtable = TRUE
    ) %>%
    kableExtra::row_spec(1:reviews_tables$kable$nrow, hline_after = TRUE) %>%
    kableExtra::row_spec(0, bold = TRUE) %>%
    kableExtra::column_spec(3:4, width = "2cm") %>%
    kableExtra::column_spec(5, width = "1.5cm") %>%
    kableExtra::column_spec(6:8, width = "3cm") %>%
    kableExtra::kable_styling(
        latex_options = c("repeat_header"),
        font_size = 5
    ) %>%
    kableExtra::landscape()
```
